## Conditional statements: `if,if/else,ifelse`

### Standard syntax

```{r if, eval = FALSE}
if (condition) { 
  expr_1
} else {
  expr_2
}
```

### Vectorial form

```{r ifelse, eval = FALSE}
ifelse(condition, a, b)
```

### Remarks

- `condition` is logical, so use `&`, `|`, `!`, etc. 
- `else`  is optional
- `elseif` allows imbricating statements


## Conditional statements: example

```{r, conditional_statement_example}
partiel <- 11
DS <- 14
if (partiel > 6 & mean(DS,partiel) > 10) {
    cat("\nreçu(e).")
} else {
    cat("\nrecalé(e).")
}
```

### Exercice
Use the vectorial `ifelse` to  send the full vector of results

```{r conditional_statement_example_data}
partiel <- c(11,5,6,12,9,8,14)
DS <- c(14,16,12,12,19,12,7)
```

\pause

```{r conditional_statement_example_soluce}
ifelse(partiel > 6 & rowMeans(cbind(DS,partiel)) > 10, "reçu(e)", "recalé(e)")
```

## Conditional statement: `switch`

### Syntax

```{r switch_syntax, eval = FALSE}
switch (expr,
 expr_1 = do_1,
 ...,
 expr_n = do_n,
 do_default
) 
```

### Remarks

- `expr` is either an integer or a character
-  if an integer with value $i$, the $ith$ expression `do_i` is evaluated
-  if a string the expression `do_i` so that `expr == expr_i` is evaluated

## `switch`: examples 

### `integer` form

```{r switch_example1}
expr <- 2
switch(expr, cat("My value is 1"), cat("My value is 2"))
```

```{r switch_example2, eval = FALSE}
expr <- 3
switch(expr, cat("My value is 2"), cat("My value is 2"))
```

```{r switch_example2_answer, echo = FALSE}
expr <- 3
switch(expr, cat("My value is 2"), cat("My value is 2"))
```

### `character` form

```{r switch_example3}
stat <- "variance"
f_stat <- switch(stat,
    "mean"  = mean,
    "variance" = var,
NULL)
f_stat(1:10)
```


