## loop statement: `for`

### Syntax

```{r for_syntax, eval = FALSE}
for (var in set) {
  expr(var)
}
for (var in set) # avoid this syntax!!
  expr(var)
for (var in set) expr(var)
```

### Remarks

- `var` is the incremented variable
- `set` is a vector of the successive values
- generally slow compared to matricial/vectorize operation

## `for` loop: examples

### Example: C/C++ like

```{r for_example}
for (i in sample(1:5)) cat(i)
v <- numeric(7)
for (i in seq_along(v))  v[i] <- i*3
```

### Exercice:  
Use a for loop to display the colnames of the data frame `iris` which are not a factor, by completing the follwoing piece of code

\pause

```{r for_iris_soluce}
data(iris)
for (nom in colnames(iris)) {
  if (!is.factor(iris[,nom])) cat("",nom)  
}
```
\pause

A more R-style way to do that is

```{r for_iris_correct_soluce}
cat(colnames(iris)[!sapply(iris, is.factor)])
```

## Loop statement: `while, repeat`

### Syntax

```{r while_repeat_syntax, eval = FALSE}
while (condition) {
  expr
}
repeat {
  expr
}
```

### Remarks

- avoid imbrication (slow)
- can be interrupted/controlled with with `break`/`next`

```{r while_example, eval = FALSE}
repeat {
  expr
  if (condition) {break}
}
while (condition1){
  expr_1
  if (condition2) {next}
  expr_2
}
```
