## Anonymous function

### Definition
A function that does not deserve a name, defined 'on the fly' during its use
```{r anonymous_syntax_equivalent}
(function(x) (x^2))(2)
f <- function(x) {x^2}
f(2)
```

### Remark
- generally very short with few arguments
- it style owns an environment, formals and body:

```{r}
formals(function(x) (x^2))
body(function(x) (x^2))
environment(function(x) (x^2))
```

- mostly used in conjunction with `lapply`-like functionals

```{r anonymous_syntax}
unlist(lapply(datasets::iris, function(x) length(unique(x))))
```

## Exercises on `lapply`

### Exercise 1

Use the closure `power` to generate various exponentation functions that you will store in a list. Use a functionals to compute the exponents of numbers of your choice. 

### Exercise 2

Consider the dataset `datasets::mtcars`. Use `lapply` and an anonymous function to find the coefficient of variation (`sd(x)/mean(x)`) on each column of the dataset.

### Exercise 3
 
Suppose we want to predict `mpg` (consumption) from the regressors `disp` (engine size) and `wt` (weight). We test several linear models whose corresponding `R` formulae are
- `mgp ~ 1 + disp`
- `mgp ~ I(1/disp)`
- `mgp ~ 1 + I(1 / disp) + wt`

Use ` lapply` to adjust linear models with such formulaes and extract the coefficient of determination ($R^2$).