## Functional for `matrix` and `arrays`: `apply`

### Definition
Applies a function along a dimension of an array (row/columns of matrix).
```{r apply_syntax, eval = FALSE}
apply(array, dim, FUN, ...)
```

### Example
```{r apply_example}
mat <- matrix(1:6, 2, 3)
apply(mat, 2, max)
arr <- array(1:12, c(2,3,2))
apply(arr, 3, colMeans)
```

## Other array functionals: `sweep`

### Definition
'Sweep out' a summary statistic along a dimension of an array for a given function
```{r sweep_syntax, eval = FALSE}
sweep(array, dim, stat, FUN, ...)
```

```{r load_iris, include = FALSE}
data(iris)
```

### Example
```{r sweep_iris, out.width=".6\\textwidth"}
out <- sweep(iris[, 1:4], 2, colMeans(iris[, 1:4]), "-") ## center
out <- sweep(out, 2, sqrt(colSums(out^2)/(nrow(out) - 1)), "/") ## scale
iris_sc <- data.frame(out, Species = iris$Species)
GGally::ggpairs(iris_sc, columns = 1:4, ggplot2::aes(colour = Species))
```


## Other array functionals: `outer`

### Definition
```{r outer_syntax, eval = FALSE}
outer(array1, array2, FUN, ...)
```

### Example
The more basic example is the kronecker product, but `FUN` can be anything!
```{r outer_example}
outer(1:3, 1:4, "*")
1:3 %o% 1:4

```


## Grouped functional: `tapply`

### Definition

Applies a function on a vector partioned by a factor: combine a `split` + `lapply` operation

```{r, include = FALSE}
data(iris)
```

### Example 
```{r tapply_iris}
with(iris, tapply(Sepal.Length, Species, mean)) # readable
with(iris, lapply(split(Sepal.Length, Species), mean)) # still ok (I think)
stat <- c() # less readable (and naming is lost)
for (l in levels(iris$Species))
  stat <- c(stat, mean(iris$Sepal.Length[iris$Species == l]))
stat
```

