## Cousins of `lapply`: vector ouputs

`sapply` and `vapply` extend ` lapply` by simplifying the output to an atomic vector rather than a list
- `sapply` guesses the types
- `vapply` uses a user argument

```{r sapply}
sapply(datasets::iris, is.numeric)
vapply(datasets::iris, is.numeric, logical(1))
unlist(lapply(datasets::iris, is.numeric))  ## equivalent
```

### Remarks
- `sapply` is very permissive and always find a way to output something
- `vapply` will throw an error if the required operation is not possible

\rsa `sapply` should be avoid when writing function as it can mask and propagate important error.

## Cousins of `lapply`: repeated evaluation

Sometimes a loop repeats the same operation that does not need the iteration label, for instance when one replicate several simulation involving randomness.

### Definition
```{r replicate_syntax, eval = FALSE}
replicate(number_of_repetition, {expression}, simplify = "array")
```

### Exercise
Use `replicate` to generate 100 bootstrap samples of the `iris` dataset stocked as a list.
\pause
```{r replicate_example}
n <- nrow(datasets::iris)
boots <- replicate(100, datasets::iris[sample.int(n, n, replace=TRUE), ], simplify = FALSE)
```



## Cousins of `lapply`: multiple inputs




