## Cousins of `lapply`: vector ouputs

`sapply` and `vapply` extend ` lapply` by simplifying the output to an atomic vector rather than a list
- `sapply` guesses the types
- `vapply` uses a user argument

```{r sapply}
sapply(datasets::iris, is.numeric)
vapply(datasets::iris, is.numeric, logical(1))
unlist(lapply(datasets::iris, is.numeric))  ## equivalent
```

### Remarks
- `sapply` is very permissive and always find a way to output something
- `vapply` will throw an error if the required operation is not possible

\rsa `sapply` should be avoid when writing function as it can mask and propagate important error.

## Cousins of `lapply`: repeated evaluation

Sometimes a loop repeats the same operation that does not need the iteration label, for instance when one replicate several simulation involving randomness.

### Definition
```{r replicate_syntax, eval = FALSE}
replicate(number_of_repetition, {expression}, simplify = "array")
```

### Exercise
Use `replicate` to generate 100 bootstrap samples of the `iris` dataset stocked as a list.
\pause
```{r replicate_example}
n <- nrow(datasets::iris)
boots <- replicate(100, datasets::iris[sample.int(n, n, replace=TRUE), ], simplify = FALSE)
```



## Cousins of `lapply`: multiple inputs I

### Caveat
`lapply` and its vector-input variants like `sapply` and `vapply` works for a single vector to loop over.

### Example 
Suppose we want to compute the weighted mean for series of 10 couple of vectors $(x,w)\in\mathbb{R}^{2 \times 100}$  :
```{r weighted_mean_problem}
x <- replicate(5, rnorm(100      ), simplify = FALSE)
w <- replicate(5, runif(100, 0, 1), simplify = FALSE)
```

### Solution
It is possible to handle this problem with  `lapply`.
\pause
```{r lapply_weighted_mean_soluce}
unlist(
  lapply(seq_along(x), function(i) {
    weighted.mean(x[[i]], w[[i]])  
  })
)
```

## Cousins of `lapply`: multiple inputs II

A more elegant and readable solution is to rely on ` mapply` or `Map`, which let the possibility to pass several vectors to jointly loop over:

### Syntax
```{r Map_syntax, eval = FALSE}
Map(FUN, ...)
mapply(FUN, ..., MoreArgs = NULL, simplify = TRUE, USE.NAMES = TRUE)
```

### Remarks
- `Map` and ` mapply` are equivalent
- `Map` is more consistent with `lapply` (do not simplify, a bit simpler)

### Exercise
Use `Map` and `mapply` to compute the weighted means for the set $\{(x_i,w_i)\}_{i=1, \dots, 10}$

\pause 
```{r Map_weigthed_mean_soluce}
unlist(Map(weighted.mean, x, w))
```



