## For loop functional: `lapply`

### Definition
Applies a function to each element found in a vector. The vector is defined in a `R`-way, that is, it can be a list.
```{r lapply_syntax, eval = FALSE}
lapply(vector, FUN, ...)
```

### Remarks
- `lapply` is the more spred functional in `R` 
- Works on vector of _elements_, _numeric indices_ and _names_
- Most of other functionals that we will meat build on `lapply`
- Make your code _elegant_  and _easier to read_

### Implementation
The way `lapply` operates can be understood as follows:
```{r lapply_implementation, eval = FALSE}
my_lapply <-function(vector, FUN, ...) {
  res <- vector("list", length(vector))
  for (i in seq_along(vector))
    res[[i]] <- FUN(vector[[i]], ...)
  res
}
```

## Exercises on `lapply`

### Exercise 1

Use the closure `power` to generate various exponentiation functions that you will store in a list. Use a functionals to compute the exponents of numbers of your choice. 

### Exercise 2

Consider the dataset `datasets::mtcars`. Use `lapply` and an anonymous function to find the coefficient of variation (`sd(x)/mean(x)`) on each column of the dataset.

### Exercise 3
 
Suppose we want to predict `mpg` (consumption) from the regressors `disp` (engine size) and `wt` (weight). We test several linear models whose corresponding `R` formulae are
- `mgp ~ 1 + disp`
- `mgp ~ I(1/disp)`
- `mgp ~ 1 + I(1 / disp) + wt`

Use ` lapply` to adjust linear models with such formulas and extract the coefficient of determination ($R^2$).