## Functionals for list: `Reduce` and co

> ‘Reduce’ uses a binary function to successively combine the elements of a given vector 

\rsa can be use  to  post-process your  list  of simulations obtained via `mclapply` just like `do.call`

Say more... (map, Reduce)

## Example: "jacknifing" a lasso solution path
A single Lasso fit of the diabete data set
```{r Reduce_load, out.width=".4\\textwidth"}
library(glmnet)
library(lars) # the diabetes data set (part of the lars package)
data(diabetes)
x <- diabetes$x; y <- diabetes$y; n <- length(y)
lasso <- glmnet(x,y)
plot(lasso, xvar = "lambda")
```
Compute the regularization paths for all subsets, removing one individual at once
```{r Reduce_sim}
paths <- lapply(1:n, function(i) {
    glmnet(x[-i, ], y[-i], lambda = lasso$lambda)$beta
})
```

## A Reduce example: "jacknifing" a lasso solution path II

Computing the envelop around the average regularization path with Reduce
```{r Reduce_do}
mean.path <- Reduce("+", paths)/n
sdev.path <- sqrt(Reduce("+", lapply(paths, function(path) path**2))/n - 
                  mean.path**2)
```

```{r Reduce_plot, echo = FALSE}
library(ggplot2)
library(reshape2)
mean.path <- t(as.matrix(mean.path)); rownames(mean.path) <- lasso$lambda
sdev.path <- t(as.matrix(sdev.path)); rownames(sdev.path) <- lasso$lambda
dplot <- cbind(reshape2::melt(mean.path), reshape2::melt(sdev.path)[, 3])
colnames(dplot) <- c("lambda","predictor","mean","sdev")
ggobj <- ggplot(dplot, aes(x=lambda, y=mean, group=predictor, color=predictor)) + geom_smooth(aes(ymin=mean-sdev,ymax=mean+sdev))
print(ggobj + coord_trans(x="log10"))
```
