## Exercises in `dplyr` vs `base R`

[Exercises adapted from  UseR 2017 on data. table](https://user2017.sched.com/event/Aw0L/datatable-for-beginners)

```{r}
set.seed(20170703L)## toy data.frames
DF1 = data.frame(id = sample(1:2, 9L, TRUE), 
                 code = sample(letters[1:3], 9, TRUE), 
                 valA = 1:9, valB = 10:18, 
                 stringsAsFactors = FALSE)
DF2 = data.frame(id = c(3L, 1L, 1L, 2L, 3L), 
                 code = c("b", "a", "c", "c", "d"), 
                 mul = 5:1, stringsAsFactors = FALSE)
## corresponding data tibble
TB1 <- as_tibble(DF1)
TB2 <- as_tibble(DF2)
```

## Question 1

_Subset all rows where id column equals 1 & code column is not equal to "c"_

\pause

### base

```{r}
base::subset(DF1, id == 1 & code != "c")
with(DF1, DF1[id == 1 & code != "c",])
```

\pause

### dplyr

```{r}
filter(TB1, id == 1 & code != "c")
```

## Question 2

_Select valA and valB columns from DF1_

\pause 

### base R

```{r}
DF1[, c("valA", "valB")]
```

\pause 

### dplyr

```{r}
select(TB1, valA, valB)
```

## Question 3

_Get sum(valA) and sum(valB) for id > 1 as a 1-row, 2-col data.frame_

\pause 

### base R

```{r}
colSums(DF1[ DF1$id > 1, c("valA", "valB")])
```

\pause 

### dplyr

```{r}
TB1 %>% filter(id > 1) %>% select(valA, valB) %>% summarise_all(sum)
```

## Question 4

_Replace valB with valB+1 for all rows where code == "c"_

\pause 

### base R

```{r}
DF1$valB[DF1$code == "c"] = DF1$valB[DF1$code == "c"] + 1
DF1
```

\pause 

### dplyr

```{r}
mutate(TB1, valB = ifelse(code == "c", valB + 1,valB))
```

## Question 5

_Add a new column valC column with values equal to valB^2 - valA^2_

\pause 

### base R

```{r}
DF1 <- transform(DF1, valC = valB^2 - valA^2)
## DF1$valC <- DF1$valB^2 - DF1$valA^2 # alternate solution
DF1
```

### dplyr

\pause 

```{r}
TB1 <- mutate(TB1, valC = valB^2 - valA^2)
TB1
```

## Question 6

_Get sum(valA) and sum(valB) grouped by id and code (i.e., for each unique combination of id,code)_

\pause 

### base

```{r}
aggregate(.~ id + code, DF1, sum)
aggregate(DF1[, c("valA", "valB")], list(DF1$id, DF1$code), sum)
```

\pause 

### dplyr 

```{r}
TB1 %>% group_by(id, code) %>% summarise_all(sum)
```

## Question 7

_Get sum(valA) and sum(valB) grouped by id for id >= 2 & code %in% c("a", "c")_

\pause 

### base

```{r}
aggregate(.~ id , subset(DF1, id >=2 & code %in% c("a","c"), -code), sum)
```

\pause 

### dplyr

```{r}
TB1 %>% 
  group_by(id) %>% 
  filter(id >=2, code %in% c("a", "c")) %>% 
  select(-code, -valC) %>% 
  summarise_all(sum)
```

## Question 8

_Replace valA with max(valA)-min(valA) grouped by code_

\pause 

### base

```{r}
DF1 <- transform(DF1, valA = rep(tapply(valA, code, function(x) diff(range(x)))[code]))
DF1
```

\pause 

### dplyr

```{r}
TB1 <- TB1 %>% group_by(code) %>% mutate(valA= max(valA)-min(valA))
TB1
```

## Question 9

_Create a new col named valD with max(valB)-min(valA) grouped by code_

\pause 

### base

```{r}
DF1 <- transform(DF1, valD = by(DF1, code, function(x) max(x$valB) - min(x$valA))[code])
DF1
```

\pause 

### dplyr

```{r}
TB1 <- TB1 %>% group_by(code) %>% mutate(valD= max(valB)-min(valA))
TB1
```

<!-- ## Question 10 -->

<!-- _Subset DF1 by DF2 on id,code column. That is, for each row of DF2\$id, DF2\$code, get valA and valB cols from DF1. Include rows that have no matches as well._ -->

<!-- \pause  -->

<!-- ### base  -->

<!-- ```{r} -->
<!-- merge(DF1, DF2[, c("id", "code")], by = c("id", "code"), all.y=TRUE) -->
<!-- ``` -->

<!-- \pause  -->

<!-- ### dplyr -->

<!-- ```{r} -->
<!-- right_join(TB1, TB2 %>% select(id, code), by = c("id", "code"))  -->
<!-- ## inner_join to keep only rows present in tibbles, left_join to keep all rows from TB1 -->
<!-- ## anti_join to keep only rows from TB1 with no matching rows in TB2 -->
<!-- ``` -->

<!-- #### data.table -->

<!-- ```{r} -->
<!-- merge(DT1, DT2[ , .(id, code)], all.y = TRUE) -->
<!-- ``` -->

<!-- ### Question 11 -->

<!-- _Same as (10), but fetch just the first matching row of DF1 for each row of DF2\$id, DF2\$code. Exclude non-matching rows._ -->

<!-- #### base -->

<!-- ```{r} -->
<!-- merge(DF1[!duplicated(DF1[, c("id", "code")]), ], -->
<!--       DF2[, c("id", "code")], by = c("id", "code")) -->
<!-- ``` -->

<!-- #### dplyr  -->

<!-- ```{r} -->
<!-- TB1 %>% group_by(id, code) %>% slice(1) %>% ## first entry in each (id, code) group -->
<!--   inner_join(select(TB2, id, code), by = c("id", "code")) -->
<!-- ``` -->

<!-- #### data.table -->

<!-- ```{r} -->
<!-- merge(DT1[, .SD[1], by = list(id, code)], ## first entry in each (id, code) group -->
<!--       DT2[ , .(id, code)]) -->
<!-- ``` -->

<!-- ### Question 12 -->

<!-- _For every row of DF2\$id, DF2\$code that matches with DF1’s, update valA with valA\*mul._ -->

<!-- #### base  -->

<!-- ```{r} -->
<!-- transform(merge(DF1, DF2, by = c("id", "code"), all.y=TRUE), valA = valA * mul) -->
<!-- ``` -->

<!-- #### dplyr  -->

<!-- ```{r} -->
<!-- right_join(TB1, TB2, by = c("id", "code")) %>% mutate(valA = valA * mul) -->
<!-- ``` -->

<!-- #### data.table -->

<!-- ```{r} -->
<!-- DT3 <- merge(DT1, DT2, all.y = TRUE)[ , "valA" := valA * mul] -->
<!-- show(DT3) ## je ne comprends pas pourquoi il faut utiliser show pour l'affichage -->
<!-- ``` -->


<!-- ### Question 13 -->

<!-- _Add a new column val to DF1 with values from DF2\$mul where DF2\$id, DF2\$code matches with DF1’s. Rows that don’t match should have NA._ -->

<!-- #### base -->

<!-- ```{r} -->
<!-- transform(merge(DF1, DF2, by = c("id", "code"), all.x = TRUE, sort = FALSE), mul = mul) -->
<!-- ``` -->

<!-- #### dplyr -->

<!-- ```{r} -->
<!-- left_join(TB1, TB2, by = c("id", "code")) -->
<!-- ``` -->

<!-- #### data.table -->

<!-- ```{r} -->
<!-- merge(DT1, DT2, all.x = TRUE) -->
<!-- ``` -->

