## Factor conversion are slow (\texttt{nlevels})

Do not convert large vector to `factor` if you need to perform just one operation on it.

```{r nlevels, out.width = '.6\\textwidth'}
n <- 1000; K <- 10
autoplot(microbenchmark(
  factor = nlevels(factor(sample(1:K, n, rep=TRUE))),
  numeric = length(unique(sample(1:K, n, rep=TRUE))), times=1000)
)
```

## Operations on factors are fast (e.g. `nlevels`)

  Use  `factor` if  you need  repeated operations  on  the same vector.

```{r nlevels2}
nk <- 20
seq.K <- c(10,100,1000)
res <- do.call(rbind, lapply(seq.K, function(K) {
  x1 <- rep(1:K,nk)
  x2 <- factor(x1)
  out <- microbenchmark(factor  = nlevels(x2),
                        numeric = length(unique(x1)), times=1000)
  return(data.frame(method = out$expr, timings = out$time, K = factor(K)))
}))
```

```{r, echo = FALSE, out.width = '.6\\textwidth'}
print(ggplot(res, aes(x=K, y=timings, fill=method)) + geom_boxplot() + coord_trans(y="log10"))
```

## Prefer `tabulate` to  `table` whenever you can

`table`  is a  complex function  that should  not be  use for simple  operations
like counting  the occurrences  of integers  in a vector.

```{r table, out.width = '.6\\textwidth'}
n <- 1000; K <- 10
autoplot(
  microbenchmark(
    table    = table   (sample(1:K, n, rep=TRUE)),
    tabulate = tabulate(sample(1:K, n, rep=TRUE)),
  times=1000)
)
```
  