## Function arguments {.allowframebreaks}

### Calling function
Arguments can be specified 

1. by name
2. by partial name
3. by position

### Bad habits
Here are some stupid (but correct) call to `mean(x=,trim=,na.rm=)`
```{r}
mean(1:10, n = T)
mean(1:10, , FALSE)
mean(1:10, 0.05, FALSE)
mean(, TRUE, x = c(1:10, NA))
```

### Exercise
Clarify the following function calls

```{r clarify_call, eval = FALSE}
x <- sample(replace = TRUE, 20, x = c(1:10, NA))
y <- runif(min = 0, max = 1, 20)
cor(m = "k", y = y, u = "p", x = x)
```

## Default arguments

### Arguments can have default values in `R`

```{r default}
f <- function(a = 1, b = 2) c(a,b)
f()
```

\pause 

### The `missing` function

You can check wether an argument was passed or not with `missing`:

```{r missing1}
f <- function(a = 1, b = 2) c(missing(a),missing(b))
f(a)
```

Hence, you can assign a default value _a posteriori_

```{r missing2}
f <- function(a, b = 2) {
  if (missing(a)) a <- 3  
  c(a, b)
}
f()
```

## Lazy evaluation

Arguments are evaluated only if they are used, which is known as "lazy evaluation"

```{r defaultlazy}
f <- function(a = 1, b = 4*a) c(a,b)
f()
f(43)
```

Even better (or worse...)

```{r defaultsuperlazy}
f <- function(a = 1, b = d) {
  d <- 4 + 2 * a; c(a,b)
}
f()
f(4)
```

## The ... argument

The argument `...` matches any argument not otherwise matched

- useful when collecting argument to call another function
- do not need to precify the name ofd required argument
- the counterpart is that any misspelled argument is passed to `...` and show no warning

### Example: `plot`
Many argument in `plot` are passed to the `par` function that manages the graphical paramters:

```{r plot_dot, eval = FALSE}
plot(1:5, col = "red")
plot(1:5, llty = "dotted")
```

### Capturing "..."
`list()` can be used to easily captured arguments passed with `...`
```{r capture_dot}
f <- function(...) names(list(...))
f(a = 1, b = 2)
```

## Calling a function with a list I

The `do.call` function constructs and executes a function call from a name or a function and a list of arguments to be passed to it:

### Syntax
```{r do.call_syntax, eval = FALSE}
do.call(what, args, quote = FALSE, envir = parent.frame())
```

- `what` is either a function or a string for a function name
- `args` the list of arguments for the call
- `quote` is a logical specifying if the argument should be quoted
- `envir` specifies the environment of the call

### Example
```{r do.call_example}
do.call(mean, list(x = 1:10, trim = 0.05, na.rm = FALSE))
```

## Calling a function with a list II

### Exercise
Suppose the outputs of 100 simulations are stored in a list like that

```{r docallSim, echo = FALSE}
res <- replicate(100, 
  rbind(data.frame(method="lasso", mse=runif(1,.75,1) , timing=runif(1)),
    data.frame(method="ridge", mse=runif(1,.5,.75), timing=runif(1)),
    data.frame(method="bayes", mse=runif(1,.85,1) , timing=runif(1,100,200))
  ), simplify=FALSE)
```

```{r docallSim2}
class(res)
res[[1]]
length(res)
```
How would you store them in a single data frame?

\pause

```{r docallSim3}
head(do.call(rbind, res))
```
