---
title: (A bit of) Advanced R
subtitle: Part 2 - faster `R` programming
author: Julien Chiquet
institute: "http://github/jchiquet/CourseAdvancedR"
date: "Université Paris Dauphine, Juin 2018"
csl: "../resources/apa-no-doi-no-issue.csl"
output:
  beamer_presentation:
    slide_level: 2
    highlight: tango
    includes: 
      in_header: ../resources/common_preamble.tex
      before_body: ../resources/common_startup.tex
bibliography: ../resources/bibliography.bib
fontsize: 10pt
nocite: '@*'
params: 
  child_path : "../Rmd_files/"
  setup_path : "../resources/"
---

```{r setup, include = FALSE}
source(paste0(params$setup_path, "knitr_setup.R"))
```

## References

- @advr: Advanced R, retrieved from [http://adv-r.had.co.nz/](http://adv-r.had.co.nz/)
- @efficientR: efficient R programming [https://bookdown.org/csgillespie/efficientR/](https://bookdown.org/csgillespie/efficientR/)

## Prerequisites

### Data Structure in base R

  1. Atomic vector (integer, double, logical, character)
  2. Recursive vector (list)
  3. Factors
  4. Matrices and array
  5. Data Frame

\rsa Creation, Basic Operation, Manipulation, Representation

### Basic `R` programming

  1. Control Statements
  2. Functions 
  3. Basic on Functionals 

  - Advanced R, chapters I.6,  II.10,  II.11 [@advr, [http://adv-r.had.co.nz/](http://adv-r.had.co.nz/)]


# Benchmark

```{r microbenchmark, child = paste0('profiling/', c("microbenchmark.Rmd", "profr.Rmd"))}
```

# Vectorize

```{r practices, child = paste0('good_bad_practices/', c("vectorize.Rmd", "growing.Rmd"))}
```

# Parallelize

```{r parallel, child = paste0('parallel_computing/', c("intro_parallel_computing.Rmd", "parallel.Rmd"))}
```

```{r internal, child = paste0('tricks/', c("use_algebra.Rmd"))}
```

# Prefer simple objects, as `R` is a typed language

```{r types, child = paste0('types/', c("float.Rmd", "factors.Rmd", "order.Rmd"))}
```

# Mind your vocabulary: `R` fast built in function, an others

```{r vocabulary, child = paste0('vocabulary/', c("colSums_family.Rmd", "rowsum.Rmd", "algebra.Rmd", "Matrix.Rmd", "use_algebra.Rmd"))}
```

# Use `Rcpp` and C++ code

```{r Rcpp, child = paste0('Rcpp/', c("RcppArmadillo.Rmd", "RcppArmadillo2.Rmd"))}
```

## References
