---
title: (A bit of) Advanced R
subtitle: Part 1 - towards better `R`-base programming
author: Julien Chiquet
institute: Université Paris Dauphine
date: "Juin 2018"
csl: "../resources/apa-no-doi-no-issue.csl"
output:
  beamer_presentation:
    slide_level: 2
    highlight: tango
    includes: 
      in_header: ../resources/common_preamble.tex
      before_body: ../resources/common_startup.tex
bibliography: ../resources/bibliography.bib
fontsize: 10pt
---

```{r setup, child="../resources/knitr_setup.Rmd", include = FALSE}
```

## References

- @Rbase: A Language and Environment for Statistical Computing [https://www.R-project.org/](https://www.R-project.org/)
- @advr: Advanced R, retrieved from [http://adv-r.had.co.nz/](http://adv-r.had.co.nz/)
- @efficientR: efficient R programming [https://bookdown.org/csgillespie/efficientR/](https://bookdown.org/csgillespie/efficientR/)

## Prerequisites

### Data Structure in base R

  1. Atomic vector (integer, double, logical, character)
  2. Recursive vector (list)
  3. Factors
  4. Matrices and array
  5. Data Frame

\rsa Creation, Basic Operation, Manipulation, Representation

### Resources

  - Advanced R, chapters I.2, I.3 [@advr, [http://adv-r.had.co.nz/](http://adv-r.had.co.nz/)]
  - An introduction to R programmming [http://julien.cremeriefamily.info/teachings_L3BI_ISV51.html](http://julien.cremeriefamily.info/teachings_L3BI_ISV51.html)

# Function, Functionals

```{r child_appliser, child="../Rmd_files/functionals/applieser.Rmd"}
```

```{r child_doCall, child="../Rmd_files/functionals/doCall.Rmd"}
```

```{r child_Reduce, child="../Rmd_files/functionals/Reduce.Rmd"}
```

# Good and bad practices in `R`

```{r child_vectorize, child="../Rmd_files/good_bad_practices/vectorize.Rmd"}
```

```{r child_compilation, child="../Rmd_files/good_bad_practices/compilation.Rmd"}
```

```{r child_growing, child="../Rmd_files/good_bad_practices/growing.Rmd"}
```

# Benchmark your code

```{r child_microbenchmark, child="../Rmd_files/profiling/microbenchmark.Rmd"}
```

```{r child_profiling, child="../Rmd_files/profiling/profr.Rmd"}
```

# Use all your cores when needed

```{r child_intro_parallel, child="../Rmd_files/parallel_computing/intro_parallel_computing.Rmd"}
```

```{r child_parellel, child="../Rmd_files/parallel_computing/parallel.Rmd"}
```

# Tricks

```{r child_internal, child="../Rmd_files/tricks/internal.Rmd"}
```

```{r child_use_algebra, child="../Rmd_files/tricks/use_algebra.Rmd"}
```

# Remember that R is object oriented

```{r child_factor, child="../Rmd_files/good_bad_practices/factors.Rmd"}
```

```{r child_float, child="../Rmd_files/good_bad_practices/float.Rmd"}
```

```{r child_order, child="../Rmd_files/good_bad_practices/order.Rmd"}
```

# Mind your vocabulary: `R` fast built in function

```{r child_colSums, child="../Rmd_files/vocabulary/colSums_family.Rmd"}
```

```{r child_rowsum, child="../Rmd_files/vocabulary/rowsum.Rmd"}
```

```{r child_algebra, child="../Rmd_files/vocabulary/algebra.Rmd"}
```

```{r child_Matrix, child="../Rmd_files/vocabulary/Matrix.Rmd"}
```

# Interface with lower-level languages

```{r child_RcppExample1, child="../Rmd_files/Rcpp/RcppArmadillo.Rmd"}
```

```{r child_RcppExample2, child="../Rmd_files/Rcpp/RcppArmadillo2.Rmd"}
```

## References

@nocite{*}
