---
title: (A bit of) Advanced R
subtitle: Part 1 - `R`-base programming
author: Julien Chiquet
institute: "http://github/jchiquet/CourseAdvancedR"
date: "Université Paris Dauphine, Juin 2018"
csl: "../resources/apa-no-doi-no-issue.csl"
output:
  beamer_presentation:
    slide_level: 2
    highlight: tango
    includes: 
      in_header: ../resources/common_preamble.tex
      before_body: ../resources/common_startup.tex
bibliography: ../resources/bibliography.bib
fontsize: 10pt
nocite: '@*'
params: 
  child_path : "../Rmd_files/"
  setup_path : "../resources/"
---

```{r setup, include = FALSE, cahe = FALSE}
source(paste0(params$setup_path, "knitr_setup.R"))
```

## References

- @Rbase: A Language and Environment for Statistical Computing [https://www.R-project.org/](https://www.R-project.org/)
- @advr: Advanced R, retrieved from [http://adv-r.had.co.nz/](http://adv-r.had.co.nz/)

## Prerequisites

### Data Structure in base R
  1. Atomic vector (integer, double, logical, character)
  2. Recursive vector (list)
  3. Factors
  4. Matrices and array
  5. Data Frame

\rsa Creation, Basic Operation, Manipulation, Representation

### Resources
  - Advanced R, chapters I.2, I.3 [@advr, [http://adv-r.had.co.nz/](http://adv-r.had.co.nz/)]
  - An introduction to R programming [http://julien.cremeriefamily.info/teachings_L3BI_ISV51.html](http://julien.cremeriefamily.info/teachings_L3BI_ISV51.html)

## Developement environment {.allowframebreaks}

### The Rstudio API

- A full API with code, interpreter, workspace and plots
- Package developement and external code integration are easier
- Notebooks integration with Rmarkdown
- Interface with github
\rsa required tool for efficent development in `R`

### My favorites shortcuts

- `ctrl + return`: execute current selection in console
- `ctrl + 1/2/3/4`: naviguate between panels
- `ctrl + down/up`: naviguate between tabs
- `ctrl + shift + k`: knit current doccument

### 

![Screenshot of the Rstudio API](figures/rstudio)

# Control Statements

```{r control_statements, child = paste0('control_statements/', c("grouped_expressions.Rmd", "conditional_statements.Rmd", "loop_statements.Rmd")), cache = FALSE}
```

# Functions

```{r functions, child = paste0('functions/', c("functions_basics.Rmd", "lexical_scoping.Rmd", "functions_arguments.Rmd", "infixs.Rmd", "internal.Rmd", "compilation.Rmd")), cache = FALSE}
```

# Functionals

<!-- # Function, Functionals -->

<!-- ```{r functionals, child = paste0('functionals/', c("applieser.Rmd", "doCall.Rmd", "Reduce.Rmd")), cache = FALSE} -->
<!-- ``` -->

<!-- # Good and bad practices in `R` -->

<!-- ```{r practices, child = paste0('good_bad_practices/', c("vectorize.Rmd", "compilation.Rmd", "growing.Rmd"))} -->
<!-- ``` -->

<!-- # Benchmark your code -->

<!-- ```{r microbenchmark, child = paste0('profiling/', c("microbenchmark.Rmd", "profr.Rmd"))} -->
<!-- ``` -->

<!-- # Use all your cores when needed -->

<!-- ```{r parallel, child = paste0('parallel_computing/', c("intro_parallel_computing.Rmd", "parallel.Rmd"))} -->
<!-- ``` -->

<!-- # Tricks -->

<!-- ```{r internal, child = paste0('tricks/', c("internal.Rmd", "use_algebra.Rmd"))} -->
<!-- ``` -->

<!-- # Remember that R is object oriented -->

<!-- ```{r types, child = paste0('types/', c("factors.Rmd", "float.Rmd", "order.Rmd"))} -->
<!-- ``` -->

<!-- # Mind your vocabulary: `R` fast built in function -->

<!-- ```{r vocabulary, child = paste0('vocabulary/', c("colSums_family.Rmd", "rowsum.Rmd", "algebra.Rmd", "Matrix.Rmd"))} -->
<!-- ``` -->

<!-- # Interface with lower-level languages -->

<!-- ```{r Rcpp, child = paste0('Rcpp/', c("RcppArmadillo.Rmd", "RcppArmadillo2.Rmd"))} -->
<!-- ``` -->

## References {.allowframebreaks}

